Reproducible Research: Peer Assessment 1
========================================================

## Loading and preprocessing the data
```{r readData,echo=TRUE}
activityData <- read.csv("activity.csv",head = T)
head(activityData,3)
```

## What is mean total number of steps taken per day?
```{r totalStep,echo=TRUE}
activityPerDay <- split(activityData,activityData$date)
stepsPerDay <- sapply(activityPerDay, function(x) sum(x[,c("steps")], na.rm = T))
hist(stepsPerDay)

meanStep <- mean(stepsPerDay)
medianStep <-  median(stepsPerDay)

```
 - The mean total number of steps taken per day is `r meanStep`
 - The medianStep total number of steps taken per day is `r medianStep`


## What is the average daily activity pattern?
```{r meanStepsPerInterval,echo=TRUE}
stepByInterval <- split(activityData,activityData$interval)
averageSteps <- sapply(stepByInterval , function(x) mean(x[,c("steps")], na.rm = T))

interval <- activityData$interval[1:288]

maxSteps <- max(averageSteps)
which.max(averageSteps)
intervalMax <- interval[which.max(averageSteps)]

plot(interval,averageSteps,type = "l",xlab = "Interval",ylab = "Number of steps")

```

 - The `r intervalMax` 5-minute interval, on average contains the maximum number of steps

## Imputing missing values
```{r missingValues}
missNum <- sum(is.na(activityData))
filledData <- activityData
filledData[is.na(filledData)] <- 0

stepsPerDay1 <- sapply(split(filledData,filledData$date), function(x) sum(x[,c("steps")], na.rm = T))
hist(stepsPerDay1)

meanStep1 <- mean(stepsPerDay1)
medianStep1 <-  median(stepsPerDay1)

```

 - The mean total number of steps taken per day after "NA" is replaced by "0" is `r meanStep1`
 - The medianStep total number of steps taken per day after "NA" is replaced by "0" is `r medianStep1`


## Are there differences in activity patterns between weekdays and weekends?
```{r weekdays,echo=TRUE}
Sys.setlocale("LC_TIME", "English")
week <- as.Date(as.character(filledData$date))
week <- sapply(week, weekdays)
weekData <- cbind(filledData,week)

weekday <- weekData[weekData$week %in% c("Monday","Tuesday","Wednesday","Thursday","Friday"),]
weekend <- weekData[weekData$week %in% c("Saturday","Sunday"),]

head(weekday,3)
head(weekend,3)

weekdaySteps<- sapply(split(weekday,weekday$interval), function(x) mean(x[,c("steps")], na.rm = T))
weekendSteps<- sapply(split(weekend,weekend$interval), function(x) mean(x[,c("steps")], na.rm = T))

head(weekdaySteps,3)
head(weekendSteps,3)

par(mfrow = c(2,1))
plot(interval,weekdaySteps,type = "l",xlab = "Interval",ylab = "Number of steps",main = "Weekday")
plot(interval,weekendSteps,type = "l",xlab = "Interval",ylab = "Number of steps",main = "Weekend")

```
